```{r}
```


```{r}
```

---
title: Data Analytics for Immersive Environments, Pair Project Descriptive & Inferential
  Analysis of a Jungian Sandplay VR Project
author: "Shane Cunningham, Student No.D00262648"
date: "2022-11-25"
output:
  html_document: default
  pdf_document: default
---



```{r setup, include=FALSE}

# install
if(!require("tidyr")) install.packages("tidyr")
# library
library(tidyr)
library(ggplot2)

knitr::opts_chunk$set(echo = TRUE)
```

<!-- Show available data sets -->
```{r include=FALSE}
data <- read.csv("daie_ca3_data_14.csv")
attach(data)
```
<!-- attach(data) allows use of certain functions without typing data variable every time, eg. mean(pre_trial_cpss) instead of mean(data$pre_trial_cpss)  -->

<!-- Use of markdown header sizes # = H1, ## = H2, ### = H3...ect  -->
# Table of Contents
### 1. Abstract
#### 1.1 Aim and rationale
#### 1.2 Participants and setting
#### 1.3 Experiment design
#### 1.4 Results gathering
#### 1.5 Major findings
#### 1.6 Findings/implications
### 2. Introduction
#### 2.1 Topic and context
#### 2.2 Rationale
#### 2.3 Hypothesis
### 3. Method
#### 3.1 Participants
#### 3.2 Design
#### 3.3 Materials
#### 3.4 Procedure
### 4. Results
#### 4.1 Descriptive statistics
#### 4.2 Inferential statistics
#### 4.3 Statistical tests
#### 4.4 Magnitude and direction of results
### 5. Discussion
#### 5.1 Outline findings and relation to the hypothesis
#### 5.2 Limitations (if confounding variables are clearly identified by your group)
### 6. References
 
# Abstract

### Aim and rationale

### Participants and setting

### Experiment design

### Results gathering

### Major findings

### Findings/implications

# Introduction
### Topic and context

### Rationale
### Hypothesis

# Method
### Participants
### Design
### Materials
### Procedure

# Results
### Descriptive statistics
<!-- ** ** outside of text for bold text -->
#### 	**Dimensions**
<!-- dim() calls for the dimensions of the data frame -->
```{r}
dim(data)
```
The results of the dimensions check verifies that there is 150 rows and 7 columns in the data frame.

<!-- names() calls for the variable names of the data frame -->
#### **Variables**
```{r}
names(data)
```

#### **Structure**
```{r}
str(data)
```

#### **Structure**
```{r}
stripchart(post_trial_cpss, main = "Strip Chart of post_trial_cpss", pch = 21)
```

```{r}
mean(pre_trial_cpss)
mean(post_trial_cpss)

mean(pre_trial_or)
mean(post_trial_or)
```

### Inferential statistics
### Statistical tests
### Magnitude and direction of results

# Discussion
### Outline findings and relation to the hypothesis
### Limitations (if confounding variables are clearly identified by your group)

# References











